### 2020-06-30 Documents/ESA/sections/Intro.tex
removed aux files

    Importantly, the study will seek to understand the guarantees that can be
    placed on the safety of such systems in terms of their stability and
    constraint satisfaction. If it is possible to determine, a priori, the decision making
    behaviour of a population through its learning dynamics in terms of known quantities (e.g. the
    agent parameters), then the system may be considered safe. Similarly, if it can be shown
    to be robust, and satisfy desired constraints (e.g. controls lying within desired limits), then
    we may be assured of its long-term safety. In doing so, we can ensure
    that a user can have confidence in the system's decision making and manipulation.

>>>>

\paragraph{Relevance to Safe and Trusted AI} This study will seek to understand the guarantees that can be
    placed on the safety of such systems in terms of their stability
    and constraint satisfaction. If it is possible to determine, a
    priori, the decision making behaviour of a population through its
    learning dynamics in terms of known quantities (e.g. the agent
    parameters), then the system may be considered safe. Similarly, if
    it can be shown to be robust, and satisfy desired constraints
    (e.g. controls lying within desired limits), then we may be
    assured of its long-term safety. In doing so, we can ensure that a
    user can have confidence in the system's decision making and
    manipulation.
